\documentclass{myarticle}

\title{\textbf{\href{http://dx.doi.org/10.1139/cgj-2013-0262}{Transformations and correlations among some clay parameters - the global database}\\一些黏土参数之间的转换和相关性 - 全球数据库}}
\date{\today}
\author{Jianye Ching\thanks{
    \textbf{J. Ching}. Department of Civil Engineering, National Taiwan University, Taiwan.
} ~and Kok-Kwang Phoon\thanks{
    \textbf{K.-K. Phoon}. Department of Civil and Environmental Engineering, National University of Singapore, Singapore.
}\thanks{
    \textbf{Corresponding author}: Jianye Ching (e-mail:jyching@gmail.com)
}}

\begin{document}

\maketitle

\section*{Abstract 摘要}

\begin{Parallel}{0.60\textwidth}{}
    \ParallelLText
    {
        This study compiles a large database of 10 clay parameters (labeled as CLAY/10/7490) from 251 studies, covering clay data from 30 regions or countries worldwide. Hence, the range of data covered by this “global” database is broader than that underlying the calibration of existing transformation models in the literature. These transformation models relate test measurements (e.g., cone tip resistance) to appropriate design parameters (e.g., undrained shear strength). The correlation behaviours exhibited by the database among the 10 clay parameters are consistent with those exhibited by existing transformation models in the literature. The biases and transformation uncertainties of these transformation models with respect to the global database are calibrated. It is found that more recent transformation models are less biased and that the transformation uncertainties are typically fairly large. Such large transformation uncertainties are further reduced by incorporating secondary input parameters, such as plasticity index or sensitivity. In a companion paper written by the same authors, a 10-dimensional multivariate probability distribution coupling these clay parameters is constructed from CLAY/10/7490 and a useful application involving updating the entire bivariate probability distribution of two design parameters from three separate measurements is presented.

        \textbf{Key words: }clay properties, correlations, transformation models, database, statistics.
    }
    \ParallelRText
    {
        本研究汇编了来自251个研究的10个粘土参数（标记为CLAY/10/7490）的大型数据库，涵盖了来自全球30个地区或国家的粘土数据。因此，该“全球”数据库所涵盖的数据范围比文献中现有转换模型的标定所依据的范围要广。这些转换模型将测试测量值（例如，锥头阻力）与适当的设计参数（例如，不排水的剪切强度）相关联。数据库显示的10个黏土参数之间的相关行为与文献中现有的转换模型所显示的相关行为一致。这些转换模型相对于全局数据库的偏差和转换不确定性已得到校准。结果发现，更新的转换模型偏差较小，并且转换不确定性通常相当大。通过合并次级输入参数（例如可塑性指数或灵敏度），可以进一步降低如此大的变换不确定性。在同一位作者撰写的伴随论文中，从CLAY/10/7490构建了耦合这些黏土参数的10维多元概率分布，并提出了一个有用的应用程序，其中涉及从三个独立的测量值更新两个设计参数的整个双变量概率分布。

        \textbf{关键词：}黏土特性，相关性，转换模型，数据库，统计数据。
    }
\end{Parallel}

\input{sections/section-1.tex}
\input{sections/section-2.tex}
\input{sections/section-3.tex}
\input{sections/section-4.tex}
\input{sections/section-5.tex}
\input{sections/section-6.tex}
\input{sections/section-7.tex}

\begin{appendix}
    \section{Summary of database CLAY/10/7490 数据库CLAY/10/7490概览}\label{appendix:a}
    \input{tables/table-a1.tex}
\end{appendix}

\bibliographystyle{plainnat} % gbt7714-author-year gbt7714-numerical
\bibliography{Ching2014.bib}

\end{document}